FMA: A Dataset For Music Analysis

### 2017-07-12 fma.tex
update reviewer 1

\documentclass{article}
\usepackage[T1]{fontenc} \usepackage[utf8]{inputenc}
\usepackage[svgnames]{xcolor}
\usepackage[bookmarks=false,colorlinks=true,allcolors=DarkBlue]{hyperref} % MidnightBlue, NavyBlue, DarkBlue, Maroon
\usepackage{ismir,amsmath}
\usepackage{graphicx} \graphicspath{{figs/}}
\usepackage{booktabs, threeparttable, tabularx}
\usepackage{enumitem} \setlist{itemsep=0pt,topsep=0pt,parsep=0pt,partopsep=0pt}
\usepackage{scrextend}

@@

\multauthor
{Michaël Defferrard$^\dagger$ \hspace{.6cm} Kirell Benzi$^\dagger$ \hspace{.6cm} Pierre Vandergheynst$^\dagger$ \hspace{.6cm} Xavier Bresson$^\ddagger$}
{
	$^\dagger$LTS2, EPFL, Switzerland \hspace{0.4cm}
	$^\ddagger$SCSE, NTU, Singapore \hspace{0.4cm}
	{\small Work conducted when XB was at EPFL.}\\
	{\tt\small \{michael.defferrard,kirell.benzi,pierre.vandergheynst\}@epfl.ch, xbresson@ntu.edu.sg}
}

%\multauthor
%{$^1$ \hspace{1cm} Second author$^1$ \hspace{1cm} Third author$^2$} { \bfseries{Fourth author$^3$ \hspace{1cm} Fifth author$^2$ \hspace{1cm} Sixth author$^1$}\\
%  $^1$ Department of Computer Science, University , Country\\
%$^2$ International Laboratories, City, Country\\
%$^3$  Company, Address\\
%{\tt\small CorrespondenceAuthor@ismir.edu, PossibleOtherAuthor@ismir.edu}
%}
%\def\authorname{First author, Second author, Third author, Fourth author, Fifth author, Sixth author}

%\threeauthors
%  {First Author} {Affiliation1 \\ {\tt author1@ismir.edu}}
%  {Second Author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
%  {Third Author} {Affiliation3 \\ {\tt author3@ismir.edu}}

%% To make customize author list in Creative Common license, uncomment and customize the next line
\def\authorname{Michaël Defferrard, Kirell Benzi, Pierre Vandergheynst, Xavier Bresson}

@@

% about 150-200 words.
\begin{abstract}
We introduce the Free Music Archive (FMA), an open and easily accessible dataset suitable for evaluating several tasks in MIR, a field concerned with browsing, searching, and organizing large music collections.
The community's growing interest in feature and end-to-end learning is however restrained by the limited availability of large audio datasets.
The FMA aims to overcome this hurdle by providing \size GiB and \tduration days of Creative Commons-licensed audio from \ntracks tracks from \nartists artists and \nalbums albums, arranged in a hierarchical taxonomy of \ngenres genres.
It provides metadata like song title, album, artist and genres; user data like play counts, favorites, and comments; free-form text like description, biography, and tags; together with full-length, high-quality audio, and some pre-computed features. We propose a train/validation/test split and three subsets: a genre-balanced set of 8,000 tracks from 8 major genres, a genre-unbalanced set of 25,000 tracks from 16 genres, and a 98 GiB version with clips trimmed to 30s.
This paper describes the dataset and how it was created, discuss some suitable MIR tasks, and evaluates some baselines for genre recognition.
Code, data, and usage examples are available at \url{\weblink}.
\end{abstract}

@@

% hook
While the development of new mathematical models and algorithms to solve challenging real-world problems is obviously of first importance to any field of research, evaluation and comparison to the existing state-of-the-art is necessary for a technique to be widely adopted by research communities. Such tasks require open benchmark datasets to be reproducible. % to achieve their purpose, which are sometimes challenging to collect and share.
In computer vision, the community has developed over the years established benchmark datasets such as \href{http://yann.lecun.com/exdb/mnist/}{MNIST} \cite{mnist}, \href{https://www.cs.toronto.edu/~kriz/cifar.html}{CIFAR} \cite{cifar}, or \href{http://www.image-net.org}{ImageNet} \cite{imagenet}. These datasets are free, legal, easily available, and have proved essential to advance the field. The most celebrated example, the \href{http://www.image-net.org/challenges/LSVRC/2012/}{ILSVRC2012 challenge} on an unprecedented ImageNet subset of 1.3M images \cite{imagenet_challenge}, demonstrated the power of deep learning (DL), which won the competition with an 11\% accuracy advantage over the second best \cite{convnet_imagenet}, and unlocked incredible achievements in both fields \cite{dl}.

\begin{table}[t]
	\centering
	\begin{threeparttable}
	\begin{tabular}{l@{ }rrcc}
		\toprule
		dataset\tnote{1} & \#clips & \#artists & year & audio \\
		\midrule
		\href{https://staff.aist.go.jp/m.goto/RWC-MDB/}{RWC} \cite{RWC} & 465 & - & 2001 & yes \\
		\href{http://calab1.ucsd.edu/~datasets/cal500/}{CAL500} \cite{cal500} & 500 & 500 & 2007 & yes \\
		\href{http://mtg.upf.edu/ismir2004/contest/tempoContest/node5.html}{Ballroom} \cite{ballroom} & 698 & - & 2004 & yes \\
		\href{https://marsyasweb.appspot.com/download/data_sets/}{GZTAN} \cite{gtzan} & 1,000 & $\sim300$ & 2002 & yes \\
		\href{http://www.cp.jku.at/datasets/musiclef/}{MusiClef} \cite{musiclef} & 1,355 & 218 & 2012 & yes \\
		\href{https://labrosa.ee.columbia.edu/projects/artistid/}{Artist20} \cite{artist20} & 1,413 & 20 & 2007 & yes \\
		\href{http://ismir2004.ismir.net/genre_contest/}{ISMIR2004} & 1,458 & - & 2004 & yes \\
		\href{http://www-ai.cs.uni-dortmund.de/audio.html}{Homburg} \cite{homburg} & 1,886 & 1,463 & 2005 & yes \\  % GarageBand
		103-Artists \cite{103artists} & 2,445 & 103 & 2005 & yes \\
		\href{http://www.seyerlehner.info/index.php?p=1_3_Download}{Unique} \cite{unique} & 3,115 & 3,115 & 2010 & yes \\
		\href{http://www.seyerlehner.info/index.php?p=1_3_Download}{1517-Artists} \cite{1517artists} & 3,180 & 1,517 & 2008 & yes \\
		\href{http://www.ppgia.pucpr.br/~silla/lmd/}{LMD} \cite{lmd} & 3,227 & - & 2007 & no \\
		\href{http://anasynth.ircam.fr/home/media/ExtendedBallroom}{EBallroom} \cite{extballroom} & 4,180 & - & 2016 & no\tnote{2} \\
		\href{https://labrosa.ee.columbia.edu/projects/musicsim/uspop2002.html}{USPOP} \cite{uspop} & 8,752 & 400 & 2003 & no \\
		\href{http://calab1.ucsd.edu/~datasets/cal10k/}{CAL10k} \cite{cal10k} & 10,271 & 4,597 & 2010 & no \\ % Swat10k
		\href{http://mirg.city.ac.uk/codeapps/the-magnatagatune-dataset}{TagATune} \cite{magnatagatune} & 25,863\tnote{3} & 230 & 2009 & yes\tnote{4} \\ % MagnaTagATune
		\href{http://jmir.sourceforge.net/index_Codaich.html}{Codaich} \cite{codaich} & 26,420 & 1,941 & 2006 & no \\ % paper 20,849
		\bf \href{\weblink}{FMA} & \bf \ntracks & \bf \nartists & \bf 2017 & \bf yes \\
		\href{http://www.omras2.org/}{OMRAS2} \cite{omras} & 152,410 & 6,938 & 2009 & no \\
		\href{https://labrosa.ee.columbia.edu/millionsong/}{MSD} \cite{msd} & 1,000,000 & 44,745 & 2011 & no\tnote{2} \\
		\href{https://research.google.com/audioset/}{AudioSet} \cite{audioset} & 2,084,320 & - & 2017 & no\tnote{2} \\
		\bottomrule
	\end{tabular}
	\begin{tablenotes}
		% 103-Artists is also known as DB-L, Extended Ballroom
		\item[1] Names are clickable links to datasets' homepage.
		\item[2] Audio not directly available, can be downloaded from \href{http://www.ballroomdancers.com}{ballroomdancers.com}, \href{https://www.7digital.com}{7digital.com}, \href{https://www.youtube.com}{youtube.com}.
		\item[3] The 25,863 clips are cut from 5,405 songs.
		\item[4] Low quality 16 kHz, 32 kbit/s, mono mp3.
	\end{tablenotes}
	\end{threeparttable}
	\caption{Comparison with some other datasets.} % Genre classification datasets.
	\label{tab:datasets}
\end{table}
% Lists of datasets:
% * http://www.audiocontentanalysis.org/data-sets/
% * A Survey of Evaluation in Music Genre Recognition

\begin{table*}[t]
	\centering
	\begin{threeparttable}
		\begin{tabular}{l@{\hspace{2.7em}}r
			@{\hspace{2.7em}}>{$}r<{$}
			@{}>{${}={}$}c@{}
			>{$}l<{$}
			@{\hspace{2.7em}}>{$}c<{$}
			@{\hspace{2.7em}}c@{\hspace{2.7em}}c}
		\toprule
		dataset & \#samples & \multicolumn{3}{c}{dimensionality} & \multicolumn{3}{c}{size} \\
		\cmidrule{6-8}
				&           & \multicolumn{3}{c}{}               & \text{volume} & [GiB] & \#days \\
		\midrule
		\href{http://mirg.city.ac.uk/codeapps/the-magnatagatune-dataset}{MagnaTagATune} \cite{magnatagatune} &
			25,863 & 29\cdot16\cdot10^3\cdot1 && 4.6\cdot10^5 & 1.2\cdot10^{10} & 3 & 8.7 \\
		\href{https://research.google.com/audioset/}{AudioSet} \cite{audioset} \tnote{1} &
			2,084,320 & 10\cdot44\cdot10^3\cdot2 && 8.8\cdot10^5 & 1.8\cdot10^{12} & 776 & 241 \\
		\href{https://labrosa.ee.columbia.edu/millionsong/}{MSD} \cite{msd} \tnote{2} &
			1,000,000 & 49\cdot27\cdot10^3\cdot2 && 2.6\cdot10^6 & 2.6\cdot10^{12} & 625 & 567 \\
		\href{\weblink}{FMA} \tnote{2} &
			\ntracks & \aduration\cdot44\cdot10^3\cdot2 && 2.4\cdot10^7 & 2.6\cdot10^{12} & \size & \tduration \\
		\midrule
		\href{http://yann.lecun.com/exdb/mnist/}{MNIST} \cite{mnist} &
			70,000 & 28\cdot28\cdot1 && 7.8\cdot10^2 & 5.5\cdot10^{7\phantom0} & 0.011 & - \\
		\href{https://www.cs.toronto.edu/~kriz/cifar.html}{CIFAR-10} \cite{cifar} &
			60,000 & 32\cdot32\cdot3 && 3.0\cdot10^3 & 1.8\cdot10^{8\phantom0} & 0.16 & - \\
		\href{http://www.image-net.org/challenges/LSVRC/2012/}{ILSVRC 2012-17} \cite{imagenet_challenge} \tnote{3,4} &
			1,341,167 & 482\cdot415\cdot3 && 6.0\cdot10^5 & 8.0\cdot10^{11} & 100 & - \\
		\href{http://www.image-net.org}{ImageNet} \cite{imagenet} \tnote{3} &
			14,197,122 & 482\cdot415\cdot3 && 6.0\cdot10^5 & 8.5\cdot10^{12} & 1000 & - \\
		\bottomrule
	\end{tabular}
	\begin{tablenotes}
		\item[1] \href{https://support.google.com/youtube/answer/6039860}{YouTube recommended} sample rate for music videos. Size in GiB calculated for mp3 encoded at 320 kbit/s.
		\item[2] Average duration and sample rate. Most excerpts from \href{https://www.7digital.com}{7digital} are 30 or 60s and 22 or 44kHz \cite{msd_features}.
		\item[3] Average resolutions. Most applications resize or crop to $256\cdot256$ for a scale of $2.6\cdot10^{11}$ and $2.8\cdot10^{12}$.
		\item[4] Object detection / classification task. It is the most used dataset for image classification.
	\end{tablenotes}
	\end{threeparttable}
	\caption{Comparison between the largest public audio and image datasets. Dimensionality is (length $\cdot$ sample rate $\cdot$ \#channels) for audio and (xdim $\cdot$ ydim $\cdot$ \#channels) for images. Volume is the number of samples times the dimensionality. Size is for a directory containing all \texttt{.mp3} or \texttt{.jpg} in GiB, an indication of the quantity of information affected by the size and diversity of the data. The last column is the number of days necessary to listen to the whole available audio.}
	\label{tab:size}
\end{table*}
% Magnatagature dead links: http://tagatune.org/Datasets.html http://tagatune.org/Magnatagatune.html
% Announcement: https://musicmachinery.com/2009/04/01/magnatagatune-a-new-research-data-set-for-mir/
% Robin: Alors il télécharge aussi des clips audios de 10 secondes, non-compressé et à 48 kHz pour un total de 4 Terabytes! Donc environ 8x la taille de ton dataset il semble.
% uncompressed: 2084320*10*48e3*2*2 / 1024**4 = 3.6
% 320 kbit/s mp3: 2084320*10*320e3 / 8 / 1024**3 = 776

@@

\begin{table}
	\centering
	\begin{tabular}{|llll|}
		\hline
		track\_id & title & number & \\
		information & language\_code & license & \\
		composer & publisher & lyricist & \\
		genres & genres\_all & genre\_top & \\
		duration & bit\_rate & interest & \\ %samplerate \\
		\#listens & \#comments & \#favorites & tags \\
		date\_created & date\_recorded & & \\
		\hline
		album\_id & title & type & \#tracks \\
		information & engineer & producer & \\
		\#listens & \#comments & \#favorites & tags \\
		date\_created & date\_released & & \\
		\hline
		artist\_id & name & & \\
		bio & members & \multicolumn{2}{l|}{associated\_labels} \\
		website & wikipedia\_page & \multicolumn{2}{l|}{related\_projects} \\
		location & longitude & latitude & \\
		& \#comments & \#favorites & tags \\
		date\_created & active\_year\_end & \multicolumn{2}{l|}{active\_year\_begin} \\
		\hline
	\end{tabular}
	\caption{List of available per-track, per-album and per-artist metadata, i.e. the columns of \texttt{tracks.csv}.}
	%Not all of them are filled for each track.\footnote{See }
	%\texttt{albums.csv} and \texttt{artists.csv}.}
	% genres.csv ?
	\label{tab:metadata}
\end{table}

% Besides, the most influential competition in the field of music analysis organized every year is the Music Information Retrieval Evaluation eXchange (MIREX).\href{http://www.music-ir.org/mirex/wiki/}{MIREX} proposes several important music analysis challenges such as song identification, tag classification, music similarity and retrieval, etc. However, participants do not have access to neither the test set, nor the important train set. They must upload their code to a website that will be evaluated by the organizers. In other words, participants cannot train their analysis models on any part of the dataset.

% {\bf Available music datasets and their limitations.}
Unlike other modalities such as images or text for which a wealth of content is available, the lack of a large-scale, complete and easily available dataset for MIR has hindered research on data-heavy models such as DL.
\tabref{tab:datasets} lists the most common datasets used for content-based MIR.
GTZAN \cite{gtzan}, a collection of 1000 songs from 10 genres, was the first publicly available benchmark MGR dataset. As a result, despites its flaws \cite{gtzan_critic_1}, it continues to be the most used dataset for MGR \cite{mgr_eval}. The main limitations of GTZAN is its illegality, small size, and missing metadata (no user ratings or even artist name and song title). % Each song is represented by a 22,050Hz Mono 16-bit wav audio file of 30sec.
Looking at \tabref{tab:datasets}, the well-known MagnaTagATune and the Million Song Dataset (MSD) as well as the newer AudioSet appear as contenders for a large-scale reference dataset. % They however each have limitations.
MagnaTagATune, which was collected from the \href{https://magnatune.com/}{Magnatune} label and tagged using the \href{http://tagatune.org/}{TagATune} game, includes metadata, audio features and raw audio. The poor audio quality and limited number of songs does however limit its usage.
MSD and AudioSet, while legal and very large, force researchers to download audio excerpts from online services.
% Finally, Echonest reassigned the indexing of the MDS songs with its database, which henceworth makes (almost) impossible the use of the most music recent features developed by Echonest.
% Each song data is composed of high-level and medium-level audio features provided by Echonest service and metadata like artist name, song title, track genre, etc. It has its own dedicated website with related code and additional datasets.
% 2.1 million annotated 10-second sound clips associated with 527 classes. The ontology is quite broad and covers sounds from music to cars, engines or animals. 
On the other hand, the proposed dataset offers the following qualities, which in our view are essential for a reference benchmark.

% Value proposition.
\textbf{Large scale.} Large datasets are needed to avoid overtraining and to effectively learn models that incorporate the ambiguities and inconsistencies that one finds with musical categories. They are also more diverse and allows to average out annotation noise.
While FMA features less clips than MSD or AudioSet, every other dataset with readily available quality audio are two orders of magnitude smaller (\tabref{tab:datasets}).
For statistical learning algorithms, the scale of FMA is comparable to ImageNet and the most used ILSVRC (\tabref{tab:size}) and shall thus be sufficient for the foreseable future.
Note that while image datasets are larger, the amount of data is similar because of their smaller dimensionality.

@@

% Do not present like this because we might want representativeness. Which would necessarily include commercial music.
%{\bf What would be the requirements for an ideal music dataset?} \\
%(1) Availability of raw audio tracks like 30sec or more,\\
%(2) Availability of metadata such as genres, artist, title, year, lyrics, users' ratings, users' comments, etc,\\
%(3) Large-scale dataset to be able to sample the high-dimensional distribution of music genres\\
%(4) Free and easy access of the dataset,\\
%(5) Legality of the dataset, no copyright issue with e.g. open access licence.\\

>>>>

\documentclass{article}
\usepackage[T1]{fontenc} \usepackage[utf8]{inputenc}
\usepackage[svgnames]{xcolor}
\usepackage[bookmarks=false,colorlinks=true,allcolors=DarkBlue]{hyperref} % MidnightBlue, NavyBlue, DarkBlue, Maroon
\usepackage{ismir,amsmath}
\usepackage{graphicx} \graphicspath{{figs/}}
\usepackage[font=small,skip=8pt]{caption}
\usepackage{booktabs, threeparttable, tabularx}
\usepackage{enumitem} \setlist{itemsep=0pt,topsep=0pt,parsep=0pt,partopsep=0pt}
\usepackage{scrextend}

@@

\multauthor
{Michaël Defferrard$^\dagger$ \hspace{.6cm} Kirell Benzi$^\dagger$ \hspace{.6cm} Pierre Vandergheynst$^\dagger$ \hspace{.6cm} Xavier Bresson$^\ddagger$}
{
	$^\dagger$LTS2, EPFL, Switzerland \hspace{0.4cm}
	$^\ddagger$SCSE, NTU, Singapore \hspace{0.4cm}
	{\small Work conducted when XB was at EPFL.}\\
	{\tt\small \{michael.defferrard,kirell.benzi,pierre.vandergheynst\}@epfl.ch, xbresson@ntu.edu.sg}
}
\def\authorname{Michaël Defferrard, Kirell Benzi, Pierre Vandergheynst, Xavier Bresson}

@@

% about 150-200 words.
\begin{abstract}
We introduce the Free Music Archive (FMA), an open and easily accessible dataset suitable for evaluating several tasks in MIR, a field concerned with browsing, searching, and organizing large music collections.
The community's growing interest in feature and end-to-end learning is however restrained by the limited availability of large audio datasets.
The FMA aims to overcome this hurdle by providing \size GiB and \tduration days of Creative Commons-licensed audio from \ntracks tracks from \nartists artists and \nalbums albums, arranged in a hierarchical taxonomy of \ngenres genres.
It provides metadata like song title, album, artist and genres; user data like play counts, favorites, and comments; free-form text like description, biography, and tags; together with full-length, high-quality audio, and some pre-computed features. We propose a train/validation/test split and three subsets: a genre-balanced set of 8,000 tracks from 8 major genres, a genre-unbalanced set of 25,000 tracks from 16 genres, and a 98 GiB version with 30s clips.
This paper describes the dataset and how it was created, discuss some suitable MIR tasks, and evaluates some baselines for genre recognition.
Code, data, and usage examples are available at \url{\weblink}.
\end{abstract}

@@

% hook
While the development of new mathematical models and algorithms to solve challenging real-world problems is obviously of first importance to any field of research, evaluation and comparison to the existing state-of-the-art is necessary for a technique to be widely adopted by research communities. Such tasks require open benchmark datasets to be reproducible. % to achieve their purpose, which are sometimes challenging to collect and share.
In computer vision, the community has developed established benchmark datasets such as \href{http://yann.lecun.com/exdb/mnist/}{MNIST} \cite{mnist}, \href{https://www.cs.toronto.edu/~kriz/cifar.html}{CIFAR} \cite{cifar}, or \href{http://www.image-net.org}{ImageNet} \cite{imagenet}, which have proved essential to advance the field. The most celebrated example, the \href{http://www.image-net.org/challenges/LSVRC/2012/}{ILSVRC2012 challenge} on an unprecedented ImageNet subset of 1.3M images \cite{imagenet_challenge}, demonstrated the power of deep learning (DL), which won the competition with an 11\% accuracy advantage over the second best \cite{convnet_imagenet}, and enabled incredible achievements in both fields \cite{dl}.

\begin{table}[t]
	\small
	\centering
	\begin{threeparttable}
	\begin{tabular}{l@{ }rrcc}
		\toprule
		dataset\tnote{1} & \#clips & \#artists & year & audio \\
		\midrule
		\href{https://staff.aist.go.jp/m.goto/RWC-MDB/}{RWC} \cite{RWC} & 465 & - & 2001 & yes \\
		\href{http://calab1.ucsd.edu/~datasets/cal500/}{CAL500} \cite{cal500} & 500 & 500 & 2007 & yes \\
		\href{http://mtg.upf.edu/ismir2004/contest/tempoContest/node5.html}{Ballroom} \cite{ballroom} & 698 & - & 2004 & yes \\
		\href{https://marsyasweb.appspot.com/download/data_sets/}{GTZAN} \cite{gtzan} & 1,000 & $\sim300$ & 2002 & yes \\
		\href{http://www.cp.jku.at/datasets/musiclef/}{MusiClef} \cite{musiclef} & 1,355 & 218 & 2012 & yes \\
		\href{https://labrosa.ee.columbia.edu/projects/artistid/}{Artist20} \cite{artist20} & 1,413 & 20 & 2007 & yes \\
		\href{http://ismir2004.ismir.net/genre_contest/}{ISMIR2004} & 1,458 & - & 2004 & yes \\
		\href{http://www-ai.cs.uni-dortmund.de/audio.html}{Homburg} \cite{homburg} & 1,886 & 1,463 & 2005 & yes \\  % GarageBand
		103-Artists \cite{103artists} & 2,445 & 103 & 2005 & yes \\
		\href{http://www.seyerlehner.info/index.php?p=1_3_Download}{Unique} \cite{unique} & 3,115 & 3,115 & 2010 & yes \\
		\href{http://www.seyerlehner.info/index.php?p=1_3_Download}{1517-Artists} \cite{1517artists} & 3,180 & 1,517 & 2008 & yes \\
		\href{http://www.ppgia.pucpr.br/~silla/lmd/}{LMD} \cite{lmd} & 3,227 & - & 2007 & no \\
		\href{http://anasynth.ircam.fr/home/media/ExtendedBallroom}{EBallroom} \cite{extballroom} & 4,180 & - & 2016 & no\tnote{2} \\
		\href{https://labrosa.ee.columbia.edu/projects/musicsim/uspop2002.html}{USPOP} \cite{uspop} & 8,752 & 400 & 2003 & no \\
		\href{http://calab1.ucsd.edu/~datasets/cal10k/}{CAL10k} \cite{cal10k} & 10,271 & 4,597 & 2010 & no \\ % Swat10k
		\href{http://mirg.city.ac.uk/codeapps/the-magnatagatune-dataset}{MagnaTagATune} \cite{magnatagatune} & 25,863\tnote{3} & 230 & 2009 & yes\tnote{4} \\ % MagnaTagATune
		\href{http://jmir.sourceforge.net/index_Codaich.html}{Codaich} \cite{codaich} & 26,420 & 1,941 & 2006 & no \\ % paper 20,849
		\bf \href{\weblink}{FMA} & \bf \ntracks & \bf \nartists & \bf 2017 & \bf yes \\
		\href{http://www.omras2.org/}{OMRAS2} \cite{omras} & 152,410 & 6,938 & 2009 & no \\
		\href{https://labrosa.ee.columbia.edu/millionsong/}{MSD} \cite{msd} & 1,000,000 & 44,745 & 2011 & no\tnote{2} \\
		\href{https://research.google.com/audioset/}{AudioSet} \cite{audioset} & 2,084,320 & - & 2017 & no\tnote{2} \\
		\href{https://acousticbrainz.org}{AcousticBrainz} \cite{acousticbrainz} & 2,508,627\tnote{5} & - & 2017 & no \\
		\bottomrule
	\end{tabular}
	\begin{tablenotes}
		% 103-Artists is also known as DB-L, Extended Ballroom
		\item[1] Names are clickable links to datasets' homepage.
		\item[2] Audio not directly available, can be downloaded from \\ \href{http://www.ballroomdancers.com}{ballroomdancers.com}, \href{https://www.7digital.com}{7digital.com}, \href{https://www.youtube.com}{youtube.com}.
		\item[3] The 25,863 clips are cut from 5,405 songs.
		\item[4] Low quality 16 kHz, 32 kbit/s, mono mp3.
		\item[5] As of 2017-07-10, of which a subset has been linked to genre labels for the \href{http://www.multimediaeval.org/mediaeval2017}{MediaEval 2017} \href{https://multimediaeval.github.io/2017-AcousticBrainz-Genre-Task}{genre task}.
	\end{tablenotes}
	\end{threeparttable}
	\caption{Comparison between FMA and alternative datasets which can be used for genre recognition.}
	\label{tab:datasets}
\end{table}
% Lists of datasets:
% * http://www.audiocontentanalysis.org/data-sets/
% * A Survey of Evaluation in Music Genre Recognition

\begin{table*}[t]
	\centering
	\begin{threeparttable}
		\begin{tabular}{l@{\hspace{2.7em}}r
			@{\hspace{2.7em}}>{$}r<{$}
			@{}>{${}={}$}c@{}
			>{$}l<{$}
			@{\hspace{2.7em}}>{$}c<{$}
			@{\hspace{2.7em}}c@{\hspace{2.7em}}c}
		\toprule
		dataset & \#samples & \multicolumn{3}{c}{dimensionality} & \multicolumn{3}{c}{size} \\
		\cmidrule{6-8}
				&           & \multicolumn{3}{c}{}               & \text{volume} & [GiB] & \#days \\
		\midrule
		\href{http://mirg.city.ac.uk/codeapps/the-magnatagatune-dataset}{MagnaTagATune} \cite{magnatagatune} &
			25,863 & 29\cdot16\cdot10^3\cdot1 && 4.6\cdot10^5 & 1.2\cdot10^{10} & 3 & 8.7 \\
		\href{https://research.google.com/audioset/}{AudioSet} \cite{audioset} \tnote{1} &
			2,084,320 & 10\cdot44\cdot10^3\cdot2 && 8.8\cdot10^5 & 1.8\cdot10^{12} & 776 & 241 \\
		\href{https://labrosa.ee.columbia.edu/millionsong/}{MSD} \cite{msd} \tnote{2} &
			1,000,000 & 49\cdot27\cdot10^3\cdot2 && 2.6\cdot10^6 & 2.6\cdot10^{12} & 625 & 567 \\
		\href{\weblink}{FMA} \tnote{2} &
			\ntracks & \aduration\cdot44\cdot10^3\cdot2 && 2.4\cdot10^7 & 2.6\cdot10^{12} & \size & \tduration \\
		\midrule
		\href{http://yann.lecun.com/exdb/mnist/}{MNIST} \cite{mnist} &
			70,000 & 28\cdot28\cdot1 && 7.8\cdot10^2 & 5.5\cdot10^{7\phantom0} & 0.011 & - \\
		\href{https://www.cs.toronto.edu/~kriz/cifar.html}{CIFAR-10} \cite{cifar} &
			60,000 & 32\cdot32\cdot3 && 3.0\cdot10^3 & 1.8\cdot10^{8\phantom0} & 0.16 & - \\
		\href{http://www.image-net.org/challenges/LSVRC/2012/}{ILSVRC 2012-17} \cite{imagenet_challenge} \tnote{3,4} &
			1,341,167 & 482\cdot415\cdot3 && 6.0\cdot10^5 & 8.0\cdot10^{11} & 100 & - \\
		\href{http://www.image-net.org}{ImageNet} \cite{imagenet} \tnote{3} &
			14,197,122 & 482\cdot415\cdot3 && 6.0\cdot10^5 & 8.5\cdot10^{12} & 1000 & - \\
		\bottomrule
	\end{tabular}
	\begin{tablenotes}
		\item[1] \href{https://support.google.com/youtube/answer/6039860}{YouTube recommended} sample rate for music videos. Size in GiB calculated for mp3 encoded at 320 kbit/s.
		\item[2] Average duration and sample rate. Most clips from \href{https://www.7digital.com}{7digital} are 30 or 60s and 22 or 44kHz \cite{msd_features}.
		\item[3] Average resolutions. Most applications resize or crop to $256\cdot256$ for a scale of $2.6\cdot10^{11}$ and $2.8\cdot10^{12}$.
		\item[4] Object detection / classification task. It is the most used dataset for image classification.
	\end{tablenotes}
	\end{threeparttable}
	\caption{Comparison between the largest public audio and image datasets. Dimensionality is (length $\cdot$ sample rate $\cdot$ \#channels) for audio and (xdim $\cdot$ ydim $\cdot$ \#channels) for images. Volume is the number of samples times the dimensionality. Size is for a directory containing all \texttt{.mp3} or \texttt{.jpg} in GiB, an indication of the quantity of information affected by the size and diversity of the data. The last column is the number of days necessary to listen to the whole available audio.}
	\label{tab:size}
\end{table*}
% Magnatagature dead links: http://tagatune.org/Datasets.html http://tagatune.org/Magnatagatune.html
% Announcement: https://musicmachinery.com/2009/04/01/magnatagatune-a-new-research-data-set-for-mir/
% Robin: Alors il télécharge aussi des clips audios de 10 secondes, non-compressé et à 48 kHz pour un total de 4 Terabytes! Donc environ 8x la taille de ton dataset il semble.
% uncompressed: 2084320*10*48e3*2*2 / 1024**4 = 3.6
% 320 kbit/s mp3: 2084320*10*320e3 / 8 / 1024**3 = 776

@@

\begin{table}
	\small
	\centering
	\begin{tabular}{|llll|}
		\hline
		track\_id & title & number & \\
		information & language\_code & license & \\
		composer & publisher & lyricist & \\
		genres & genres\_all & genre\_top & \\
		duration & bit\_rate & interest & \\ %samplerate \\
		\#listens & \#comments & \#favorites & tags \\
		date\_created & date\_recorded & & \\
		\hline
		album\_id & title & type & \#tracks \\
		information & engineer & producer & \\
		\#listens & \#comments & \#favorites & tags \\
		date\_created & date\_released & & \\
		\hline
		artist\_id & name & & \\
		bio & members & \multicolumn{2}{l|}{associated\_labels} \\
		website & wikipedia\_page & \multicolumn{2}{l|}{related\_projects} \\
		location & longitude & latitude & \\
		& \#comments & \#favorites & tags \\
		date\_created & active\_year\_end & \multicolumn{2}{l|}{active\_year\_begin} \\
		\hline
	\end{tabular}
	\caption{List of available per-track, per-album and per-artist metadata, i.e.\ the columns of \texttt{tracks.csv}.}
	%Not all of them are filled for each track.\footnote{See }
	%\texttt{albums.csv} and \texttt{artists.csv}.}
	% genres.csv ?
	\label{tab:metadata}
\end{table}

An alternative to open benchmarking is the approach taken by evaluation challenges such as the music information retrieval evaluation exchange (MIREX) \cite{mirex}. The imposed constraint that input data cannot be made available to participants however incurs an approximately linear cost with the number of submissions as all algorithms have to be run by the organizers. By releasing this open dataset, we realize part of the vision of McFee et al.\ in ''a distributed, community-centric paradigm for system evaluation, built upon the principles of openness, transparency, and reproducibility`` \cite{mirex_critic}.

% {\bf Available music datasets and their limitations.}
Unlike other modalities such as images or text for which a wealth of content is available, the lack of a large-scale, complete and easily available dataset for MIR has hindered research on data-heavy models such as DL.
\tabref{tab:datasets} lists the most common datasets used for content-based MIR.
GTZAN \cite{gtzan}, a collection of 1000 clips from 10 genres, was the first publicly available benchmark MGR dataset. As a result, despites its flaws, it continues to be the most used dataset for MGR \cite{mgr_eval_2}. In addition to its small size, the main problems of GTZAN is mislabelling, repetitions, and distortions, as well as missing metadata (no artist name and song title) which prevent researchers to control for artists or album effects. % Each song is represented by a 22,050Hz Mono 16-bit wav audio file of 30sec.
Looking at \tabref{tab:datasets}, the well-known MagnaTagATune \cite{magnatagatune} and the Million Song Dataset (MSD) \cite{msd} as well as the newer AudioSet \cite{audioset} appear as contenders for a large-scale reference dataset. % They however each have limitations.
MagnaTagATune, which was collected from the \href{https://magnatune.com/}{Magnatune} label and tagged using the \href{http://tagatune.org/}{TagATune} game, includes metadata, audio features and raw audio. The poor audio quality and limited number of songs does however limit its usage.
MSD and AudioSet, while legal and very large, force researchers to download audio clips from online services.
% Finally, Echonest reassigned the indexing of the MDS songs with its database, which henceworth makes (almost) impossible the use of the most music recent features developed by Echonest.
% Each song data is composed of high-level and medium-level audio features provided by Echonest service and metadata like artist name, song title, track genre, etc. It has its own dedicated website with related code and additional datasets.
% 2.1 million annotated 10-second sound clips associated with 527 classes. The ontology is quite broad and covers sounds from music to cars, engines or animals. 
On the other hand, the proposed dataset offers the following qualities, which in our view are essential for a reference benchmark.

% Value proposition.
\textbf{Avoiding biases.} sampling bias TODO: reviewer 1 comment 15 \cite{mgr_eval_2}

\textbf{Large scale.} Large datasets are needed to avoid overtraining and to effectively learn models that incorporate the ambiguities and inconsistencies that one finds with musical categories. They are also more diverse and allows to average out annotation noise.
While FMA features less clips than MSD or AudioSet, every other dataset with readily available quality audio are two orders of magnitude smaller (\tabref{tab:datasets}).
For statistical learning algorithms, the scale of FMA is comparable to ImageNet and the most used ILSVRC (\tabref{tab:size}) and shall thus be sufficient for the foreseable future.
Note that while image datasets are larger, the amount of data is similar because of their smaller dimensionality.

@@

% Do not present like this because we might want representativeness. Which would necessarily include commercial music.
%{\bf What would be the requirements for an ideal music dataset?} \\
%(1) Availability of raw audio tracks like 30sec or more,\\
%(2) Availability of metadata such as genres, artist, title, year, lyrics, users' ratings, users' comments, etc,\\
%(3) Large-scale dataset to be able to sample the high-dimensional distribution of music genres\\
%(4) Free and easy access of the dataset,\\
%(5) Legality of the dataset, no copyright issue with e.g.\ open access licence.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Dataset} % The dataset, dataset, Introducing the FMA dataset
% Describe what it is, what are the metadata and features.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
